\thispagestyle{empty}

\begin{flushright}
\scriptsize Last updated: \today
\end{flushright}

{\LARGE Alexander Shabalin}\\[1cm]
Phone: \texttt{+7 921 390-82-31}\\
Email: \email{shabalyn.a@gmail.com}\\
GitHub: \url{https://github.com/projedi}\\[.1cm]
Born: March 24, 1991\\
Nationality: Russian

\section*{Education}

\years{Sep 2012 -\\ Aug 2014}
   MS in Software Engineering, St Petersburg Academic University.\\
   Thesis is titled ``Extraction from Agda into Haskell''.\\[.3cm]
\years{Sep 2008 -\\ Aug 2012}
   BS in Physics, Saint Petersburg State University.

\section*{Employment}

\years{Jun 2019 -\\ current}
  Yandex LLC, Senior Software Developer
  \begin{itemize}
    \itemsep 0cm
    \item Yandex.Cloud Network Block Device.
          C++, Go, Python.
  \end{itemize}

\years{Feb 2015 -\\ Jun 2019}
  Yandex LLC, Software Developer
  \begin{itemize}
    \itemsep 0cm
    \item Yandex.Browser GUI.
          C++, ObjC++, Python.
  \end{itemize}

\years{Jan 2014 -\\ Sep 2014}
   Agisoft LLC, Software Engineer
   \begin{itemize}
      \itemsep 0cm
      \item GUI application for visualization of 3d objects represented as octrees.
            C++, Qt, OpenSceneGraph.
      \item Reconstruction of 3d surfaces from point clouds.
            C++ (refactoring existing implementation
            \url{https://github.com/projedi/poisson-reconstruction}),
            Haskell (prototyping another algorithm).
   \end{itemize}
\years{Jun 2012 -\\ Jun 2013}
   Plaz LLC, Software Engineer
   \begin{itemize}
      \itemsep 0cm
      \item GUI application for video conferencing. C++, Qt, ffmpeg.\\
            \url{https://github.com/projedi/videochat}
      \item Library for live video stabilization. C++, OpenCV.\\
            \url{https://github.com/projedi/stabilization}
   \end{itemize}

\section*{Skills}

Programming languages: Haskell, C, C++, Java, Python, Go.

\section*{Languages}
Native language: Russian\\
Foreign languages: English - fluent
